%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work \& Extracurricular Activities}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {IT Laboratory Assistant (Part-time)} % Job title
    {Politecnico di Torino} % Organization
    {Turin, Italy} % Location
    {Mar. 2025 - Present} % Date(s)
    {
      \begin{cvitems}
        \item {Maintained Windows infrastructure and 3D printers/plotters across 3 computer labs.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Board Member (Prev. Project Manager)} % Role
    {B.E.S.T. Politecnico di Torino} % Organization
    {Turin, Italy} % Location
    {Jul. 2024 - Jun. 2026} % Date
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Directing 60+ members and 17 coordinators to organize 6 large-scale STEM events with an annual turnover exceeding €70,000.}
        \item {Led a 10-person team as Project Manager to organize "IBEC", a local engineering competition involving over 420 participants, managing corporate relations, fundraising, and logistics.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Certified Soft Skills Trainer} % Role
    {Board of European Students of Technology} % Organization
    {International} % Location
    {May 2025 - Present} % Date
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Completed 100+ hours of intensive "Train the Trainer" education to become a certified trainer for a network of European student NGOs.}
        \item {Designed and delivered 30+ hours of soft skills sessions tailored for STEM students.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Young European Ambassador \& DiscoverEU Ambassador} % Role
    {EU Neighbours East / DiscoverEU} % Organization
    {Italy, Slovenia, Poland} % Location
    {Aug. 2023 - Present} % Date
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Selected by EU-funded programs to promote knowledge about the EU and promote youth mobility.}
        \item {Delivered workshops across Italy, Slovenia, and Poland, and presented EU promotion strategies at national meetings.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}