%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Academic \& Personal Projects}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Team Member} % Role
    {Challenge@PoliTo by Firms: Hitachi Rail (Master's Course)} % Project Title
    {Politecnico di Torino} % Location
    {Feb. 2026 - Jun. 2026} % Date
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Selected via the "Percorso Intraprendenti" honours programme to participate in a Master's level corporate challenge.}
        \item {Collaborating in a multidisciplinary team to develop a Generative AI model for smart synchronization across hybrid (cloud and on-premise) railway software systems.}
        \item {Designing a natural language query system to automate DevOps synchronization, identify discrepancies, and manage safe updates in operational and test environments.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Creator \& Web Developer} % Role
    {"Liceo in 360°" - Virtual Reality Campus Tour} % Project Title
    {IIS IPSAR Piranesi} % Location
    {Oct. 2022 - Feb. 2023} % Date
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Architected and deployed an end-to-end web platform providing a Street View-like 360° virtual tour of the high school campus, reaching over 2,000 users in 3 months.}
        \item {Managed the complete data pipeline: from raw 360° image acquisition to advanced processing and optimization using AI upscaling and denoising tools (Topaz Gigapixel+Denoise).}
        \item {Developed the frontend using \textbf{HTML/CSS/JS}, integrating the Marzipano VR library for interactive rendering, and implemented a deployment pipeline via \textbf{GitHub}, \textbf{Netlify}, and \textbf{Firebase}.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Team Leader} % Role
    {RobotCup@School - 1st Place Winner} % Project Title
    {University of Salerno} % Location
    {Nov. 2022 - May 2023} % Date
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Developed a state-based conversational AI for the humanoid robot "Pepper" using \textbf{Choregraphe} and \textbf{Python}.}
        \item {Implemented features for real-time facial recognition, emotion detection, and demographic profiling to adapt the robot's dialogue and behavior.}
        \item {Implemented IoT integration via \textbf{MQTT} to allow the robot to control external smart devices, alongside a synchronized interactive tablet UI.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}